We believe that the project has met all of its main requirements and even has some optional features. It can be noted however that the implemented features have not achieved sufficient depth to use this game for exercising over an extended period of time. Also there were some challenges on the way, which will also be discussed here.
\\\\
A nice technical improvement would be to expand the application so it can take into account the user’s physical measurements and suggest specific exercises based on the goals of the user. The great amount of personalization would require a lot of adaptations to the current game.
\\\\
Although the exercises are measured quite allright, it is still very much possible to improve the sensors. We have received a library to serve as an example, but that was not of significant help to the accuracy of the measurements. Extended research and testing would have to be done to exclude all possibilities of cheating from the exercises and really make them measure quality instead of merely quantity.
\\\\
We would have wanted to implement a heart rate sensor to check how well the user had done a timed exercise, but we didn't get to it. The code was there for a Java-based application, but not for PhoneGap, so it was too much trouble to rewrite the whole algorithm. This would be a very nice feature to add, because it takes away a lot of the cheating possibilities.
\\\\
The application is currently causing lag after a while, because it used up quite some memory. We are not really sure where this is coming from, and we would have liked to fix this when there was more time.
\\\\
Currently, when you zoom in or out the center of the screen shifts a couple of tiles, this might be a bit annoying. To fix this we would have to set a focus point. This was not a big priority however, so it has been skipped for this version.
