\subsection{PhoneGap}

PhoneGap is an open source framework for quickly building cross-platform mobile apps using HTML5, JavaScript and CSS. It is a convenient way to develop an Android game. It also gives the possibility to eventually extend to iOS to enlarge the target audience.

\subsection{HTML 5}

HTML5 is a core technology markup language of the Internet used for structuring and presenting content for the World Wide Web. It includes detailed processing models to encourage more interoperable implementations; it extends, improves and rationalises the markup available for documents, and introduces markup and application programming interfaces (APIs) for complex web applications [6]. For the same reasons, HTML5 is also a potential candidate for cross-platform mobile applications. Many features of HTML5 have been built with the consideration of being able to run on low-powered devices such as smartphones and tablets. We have chosen for HTML 5 because it is encouraged to use that for web-based games.

 \subsection{Closure}

The Closure Library is a JavaScript library, written specifically to take advantage of the Closure Compiler, based on a modular architecture. It provides cross-browser functions for DOM manipulations and events, Ajax and JSON, as well as more high-level objects such as User Interface widgets and Controls.

The Closure Library is a broad, well-tested, modular, and cross-browser JavaScript library. You can pull just what you need from a large set of reusable UI widgets and controls, and from lower-level utilities for DOM manipulation, server communication, animation, data structures, unit testing, rich-text editing, and more.
The Closure Library is server-agnostic, and is intended for use with the Closure Compiler.
Moreover, LimeJS uses Closure. 

\subsection{Closure compiler}
The Closure Compiler is a tool for making JavaScript download and run faster. It is a true compiler for JavaScript. Instead of compiling from a source language to machine code, it compiles from JavaScript to better JavaScript. It parses your JavaScript, analyzes it, removes dead code and rewrites and minimizes what's left. It also checks syntax, variable references, and types, and warns about common JavaScript pitfalls.

\subsection{LimeJS}
\label{subsec:limejs}

LimeJS is a HTML5 game framework for building fast, native-experience games for all modern touchscreens and 
desktop browsers.
LimeJS looks like another great entry into the HTML5 gaming space.  It is based on the Google Closure library, and supports rendering to both the DOM and to the HTML5 Canvas element
\\\\
We have chosen for LimeJS because it is a well-known game creation platform for the web. It provides fast and simple rendering a has proven to be a great framework for us.

\subsection{Box2d}

Box2DJS is a JavaScript port of Box2D Physics Engine.
This is a clone of a box2d JavaScript engine which is a clone of the box2d C++ library.
PixelLab modified the library to use Google's Closure JavaScript Compiler for great compression--with the added benefit of compile-time checking.
\\\\
The use of Box2d is required by the LimeJS library.


\subsection{Cordova plugins}
\label{subsec:cordova-plugins}

\begin{itemize}
  \item \textbf{org.apache.cordova.device}
  This plugin defines a global device object, which describes the device's hardware and software. Although the object is in the global scope, it     is not available until after the device ready event.
  
  \item \textbf{org.apache.cordova.device-motion}
    This plugin provides access to the device's accelerometer. The accelerometer is a motion sensor that detects the change (delta) in movement        relative to the current device orientation, in three dimensions along the x, y, and z axis.
  \item \textbf{ org.apache.cordova.media}
    This plugin provides the ability to record and play back audio files on a device.

\end{itemize}



